Simulated Structure Factors

### 2018-07-19 Ben_Manuscripts/fourier_transforms/FT_simple_systems.tex
edits for clarification

  The atomic form factor, $f_j$ is more complicated than how it is represented
  in Equation 1 %\ref{eqn:dft}. 
  The atomic form factor is the scattering
  contribution from a single isolated atom. They are calculated as the fourier
  transform of the electron density, $\rho({\mathbf{r}})$,  which is typically
  calculated using quantum techniques. Since $\rho({\mathbf{r}})$ is a spatially
  dependent function, $f_j$ is actually a function of $\mathbf{q}$,
  $f(\mathbf{q})$. Values of $f(\mathbf{q})$ for each element are tabulated in
  the \href{http://it.iucr.org/Cb/ch6o1v0001/}{International Tables for
  Crystallography}. For $\mathbf{q}=\mathbf{0}$, the atomic form factor is equal to the 
  number of electrons possessed by the atom.

@@

  The distance, d, between peaks in the $q_y$ cross-sections of the structure
  factor is equal to $2\pi / d$ (Figure~\ref{fig:p2p_rpi}). We looked at systems
  with pores spaced 42.5 nm and 212.5 nm apart respectively.  The fundamental
  frequency appears at $q_y=0$ with magnitude equal to the number of atoms in the
  unit cell (Note that each system has a different number of atoms). Subharmonics
  follow the fundamental frequency at equally spaced intervals of width $2\pi /
  d$.

@@

  We quantified the peak width by fitting gaussian curves to the R-$\pi$ peak
  cross-sections and measuring ther full width at half maximum. Gaussian profiles
  appear to give the closest fit to the data (see Figure~\ref{fig:fwhm_fits}). We
  calculated all of FWHMs in Table~\ref{table:perfect_size_dependence} using gaussian
  fits.

  \textbf{IMPORTANT}: Note that these 'peak widths' are not the same peak widths that are seen 
  experimentally. If these showed up experimentally, they would appear as dots 
  parallel to the $q_r$ axis, crossing through R-$\pi$ and in line with R-pores.
  There is some evidence of this occuring in some of the simulations (ordered parallel 
  displaced for example).

@@

  The distance between pores does not affect the FWHM of the R-$\pi$ 'peak' in
  the $q_y$ direction.  We held the size of the unit cell constant at 42.5 x 42.5
  x 3.7 nm and varied the number of pores (and consequently, the distance between
  pores). We generated error bars for the fits based on the covariance of the
  optimized fit parameters. There is no statistical difference between the
  calculated values of each FWHM (Table~\ref{table:randomly_displaced_columns}).
  The uncertainty is lower for systems with less pores since there are more
  subharmonics available for curve fitting.

%BJC: i'm not sure about these results at the moment. I'd prefer to redo them with finer
% grids. Not sure they add much value anyways. 
%  The values of FWHM in
%  Table~\ref{table:perfect_size_dependence} are calculated using model systems
%  with 4 pores and the same box dimensions used here.

@@

  The real system is far from a perfect crystal. Here we explore the influence
  of 4 sources of disorder on the intensity of R-$\pi$:
  \begin{enumerate}
  \item Random z-displacement of columns with respect to all other columns
  \item Random rotation of layers about the z-axis
  \item Thermal noise
  \item Finite correlation between scatterers in the z-direction
  \end{enumerate}

@@

  When d = 3.7 \AA, the intensity of R-$\pi$ is equal to the number of
  scatterers per column (See Table~\ref{table:randomly_displaced_columns}).  It
  is independent of the number of pores (and hence number of columns) in the
  system. The error in the calculated intensities are comparable to the magnitude
  of the intensity because the intensity of each configuration in the trajectory
  fluctuates so much.

  \begin{table}[!htb]
  \centering
  \begin{tabular}{c c c c c}
  \toprule
  $L_z$ (\AA) & Points per column & Number of Pores &  R-$\pi$ Intensity\\ 
  \midrule
  14.8        &      4            & 4               & 3.98              \\
  18.5        &      5            & 4               & 5.05              \\
  37          &      10           & 4               & 10.08             \\
  14.8        &      4            & 9               & 4.06              \\
  18.5        &      5            & 9               & 4.78              \\
  37          &      10           & 9               & 10.19             \\
  14.8        &      4            & 16              & 4.01              \\
  18.5        &      5            & 16              & 4.95              \\
  37          &      10           & 16              & 9.61              \\
  \bottomrule
  \end{tabular}
  \caption{The intensity of R-$\pi$ is equal to the number of scatters in 
   each column when columns are uncorrelated.}\label{table:randomly_displaced_columns}
  \end{table}

  \textbf{NEW} As we allow the columns to displace less (lower values of d),
  the intensity of R-$\pi$ increases (See Figure~\ref{fig:column_displacement}).
  Once there is no displacement, the intensity of R-$\pi$ matches that of a
  perfect crystal. The intensity of R-$\pi$ in our system is likely boosted by
  correlation between columns.

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{column_displacement.png}
  \caption{As we increase the amount that columns are allowed to displaced relative
  to each other, the intensity of R-$\pi$ decreases.}\label{fig:column_displacement}
  \end{figure}

  The $q_y$ width of R-$\pi$ is infinite when columns are randomly displaced in
  the z-direction. We attempted to measure the FWHM of the system with randomly
  displaced columns containing 4 pores and $L_z = 37$. The cross-section
  (Figure~\ref{fig:random_columns_qy}) shows non-decaying noise centered near 10,
  the same R-$\pi$ intensity in Table~\ref{table:randomly_displaced_columns}. The 
  angle averaged pattern (Figure~\ref{fig:random_columns_rzplot}) further illustrates
  the diffraction lines which characterize this type of system.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_columns_qy.png}
  \caption{}\label{fig:random_columns_qy}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_columns_rzplot.png}
  \caption{}\label{fig:random_columns_rzplot}
  \end{subfigure}
  \caption{}\label{fig:random_columns_rpi_width}
  \end{figure}

@@

  \begin{table}[!htb]
  \centering
  \begin{tabular}{c c c c c c}
  \toprule
  $L_z$ (\AA) & Points per column & Number of Pores & Number of Atoms & R-$\pi$ Intensity & FWHM $\AA^{-1}$ \\
  \midrule
  14.8        &      4            & 4               & 80              &  80               & 0.37           \\
  18.5        &      5            & 4               & 100             &  100              & 0.37           \\
  37          &      10           & 4               & 200             &  200              & 0.37           \\
  14.8        &      4            & 9               & 180             &  180              & 0.37           \\
  18.5        &      5            & 9               & 225             &  225              & 0.37           \\
  37          &      10           & 9               & 450             &  450              & 0.37           \\
  14.8        &      4            & 16              & 320             &  320              & 0.37           \\
  18.5        &      5            & 16              & 400             &  400              & 0.37           \\
  37          &      10           & 16              & 800             &  800              & 0.37           \\
  \bottomrule
  \end{tabular}
  \caption{The intensity of R-$\pi$ is equal to the number of scatters in
   each column when columns are uncorrelated. Note that reproducing these results requires a very fine histogram, 
   and thus a much more expensive calculation. The default binning scheme (100 bins in each dimension) gives slightly
   misleading answers.}\label{table:randomly_displaced_columns}
  \end{table}

  In all cases, the maximum intensity of R-$\pi$ is equal to the number of
  scatterers in the system and the FWHM of the $q_y$ cross-section of the
  structure factor at R-$\pi$ is 0.37 $\AA^{-1}$, just as the perfect crystal.

  \textbf{NEW} There is no major difference in the intensity of R-$\pi$ between
  a perfect crystal and a system with randomly rotated layers. In the z
  direction, R-$\pi$ remains constant since the z components of the points are
  spaced exactly 3.7 \AA apart. The maximum intensity of R-$\pi$ is at ($q_x,
  q_y, q_z$) = (0, 0, 1.7) so there is no contribution from the x or y
  components. Figure~\ref{fig:perfect_v_random_layers} shows a comparison of the
  cross-section of R-$\pi$ along $q_y=0$. On the surface it appears that there is
  a difference between them at high values of $q_y$. However, this is dependent
  on the initial configuration of the perfect crystal system. The system with
  randomly rotated layers will always look as it does if a sufficient number of
  configurations are included in the calculation of the structure factor. The
  perfect system is in agreement with the randomly rotated layer system at low
  values of $q_y$, corresponding to scatteres spaced far apart, however it begins
  to deviate at large $q_y$, where it describes the spatial relationship between
  scatterers in a single pore. In the perfect system, pores are randomly rotated
  with respect to each other (See Figure~\ref{fig:same_rotation}), so the spatial
  relationship changes each time a system is set up. It will not average out since
  each frame is exactly the same, but if enough pores are added, the 2 
  cross-sections will match (See Figure~\ref{fig:perfect_v_random_100pores}). 
  If we create a perfect crystal system where pores are duplicated and translated, but
  not rotated (See Figure~\ref{fig:same_rotation}), the subharmonics
  at large $q_y$ are quite pronounced (Figure~\ref{fig:perfect_crystal_same_rotation})
  due to the increase in ordering in the $q_y$ direction. The peaks are likely
  geometrically related to the spacing between points within pores, but it is 
  not important to get to the bottom of that here.

@@

  When we add z-direction gaussian noise to the lattice sites in the perfect
  crystal, the intensity of R-$\pi$ drops precipitously as noise is increased
  (Figure~\ref{fig:z_noise_perfect}).  However, the FWHM in the $q_y$ direction
  is not affected by this noise.

  When we add gaussian noise in the x and y directions, the intensity of
  R-$\pi$ does not change, however the FWHM sharpens with increasing noise
  (Figure~\ref{fig:xy_noise_perfect}).

@@

  When we add noise in the x and y directions, R-$\pi$ has a finite peak width
  in its $q_y$ dimension (Figure~\ref{fig:FWHM_fit_columns}), and the intensity
  stays constant. We fit a Gaussian function to the the $q_y$ cross-section in
  order to determine its FWHM. The FWHM decay is inversely proportional to the
  amount of noise added (Figure~\ref{fig:FWHM_columns}).

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{random_columns_z_noise.png}
  \caption{}\label{fig:z_noise_columns}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{random_columns_gaussian.png}
  \caption{}\label{fig:FWHM_fit_columns}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{random_columns_xy_noise.png}
  \caption{}\label{fig:FWHM_columns}
  \end{subfigure}
  \caption{(a) The intensity of R-$\pi$ decays to 1 rapidly as gaussian noise is 
   added to the system. (b) When we add noise in the x and y directions, R-$\pi$
   broaden in the y-direction with a continuous intensity distribution that can be
   fit to a gaussian. (c) This FWHM decreases as the inverse of the amount of 
   noise added.}\label{fig:columns_noise}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_layers_z_noise.png}
  \caption{}\label{fig:random_layers_z_noise}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_layers_xy_noise.png}
  \caption{}\label{fig:random_layers_xy_noise}
  \end{subfigure}
  \caption{(a) As we add noise in the z-direction, the intensity of R-$\pi$ decreases
   rapidly to 1. The FWHM decays slowly and then jumps goes to infinity (not pictured) 
   when the intensity of R-$\pi$ becomes equal to the background intensity. However one 
   could argue there is no peak at that point. (b) When we add noise in the x and y 
   directions, the intensity of R-$\pi$ does not change, but the FWHM decays slowly.}\label{fig:layers_noise}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{covariance.png}
  \caption{}\label{fig:covariance}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{correlation.png}
  \caption{}\label{fig:correlation_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{correlation_decay.png}
  \caption{}\label{fig:correlation_decay}
  \end{subfigure}
  \caption{(a) R-$\pi$ broadens in the $q_z$ direction when scatterers are correlated.
  (b) The intensity of R-$\pi$ as the variance in scatterer position increases.}\label{fig:correlation}
  \end{figure}

@@

  \begin{table}[!htb]
  \centering
  \begin{tabular}{c c c}
  \toprule
  System                         &   $\sigma_r$ ($\AA$) &   $\sigma_z$ ($\AA$) \\
  \midrule
  Sandwiched, Ordered            &      2.30            &     1.48             \\
  Parallel Displaced, Ordered    &      2.28            &     1.45             \\
  Sandwiched, Disordered         &      2.93            &     1.58             \\
  Parallel Displaced, Disordered &      2.63            &     1.65             \\
  \bottomrule
  \end{tabular}
  \caption{Thermal noise in each dimension of the center of mass of monomer
  head groups for simulated LLC systems}\label{table:com_sigmas}
  \end{table}

@@

  The intensity of R-$\pi$ is strongly dependent on the initial configuration.
  Each time a model system is generated, the initial configuration is different
  than the previous model system. The thermal noise added does not compensate
  for these differences. We ran 40 different model systems with the only 
  difference being the initial randomization. The average R-$\pi$ intensity of the 
  40 trials was 25.7 $\pm$ 9.4. This spread has important implications for the
  reproducibility of our data since there is velocity randomization during the
  initial equilibration. Also, this initial configuration dependence is not 
  very useful for analyzing trends.

@@

  A number of factors influence the shape and intensity of the R-$\pi$
  reflection. The maximum intensity of the reflection is most strongly influence
  by thermal disorder in the z-direction. The peak is broadened in the $q_y$ ($q_r$)
  direction when there is xy-direction thermal disorder in systems with randomly displaced 
  columns. The peak is broadened in the $q_z$ direction when there is a finite (non-zero)
  correlation length between scatterers.

>>>>

  The atomic form factor, $f_j$ is more complicated than how it is represented
  in Equation 1 %\ref{eqn:dft}. 
  The atomic form factor is the scattering
  contribution from a single isolated atom. They are calculated as the fourier
  transform of the electron density, $\rho({\mathbf{r}})$,  which is typically
  calculated using quantum techniques. Since $\rho({\mathbf{r}})$ is a spatially
  dependent function, $f_j$ is actually a function of $\mathbf{q}$,
  $f(\mathbf{q})$. Values of $f(\mathbf{q})$ for each element are tabulated in
  the \href{http://it.iucr.org/Cb/ch6o1v0001/}{International Tables for
  Crystallography}. For $\mathbf{q}=\mathbf{0}$, the atomic form factor is equal to the 
  number of electrons possessed by the atom. In order to appropriately incorporate
  the atomic form factor, one can model each atom as a gaussian sphere of electron
  density whose center has a magnitude equal to the atom's atomic weight.

@@

  The distance between peaks in the $q_y$ cross-sections of the structure
  factor is equal to $2\pi / d$ (Figure~\ref{fig:p2p_rpi}), where d is the
  distance between pores. We looked at systems with pores spaced 42.5 nm and
  212.5 nm apart respectively. The fundamental frequency appears at $q_y=0$ with
  magnitude equal to the number of atoms in the unit cell (Note that each system
  has a different number of atoms). Subharmonics follow the fundamental frequency
  at equally spaced intervals of width $2\pi / d$.

@@

  We fit curves to the peaks of the cross-section of $q_y$ and measurd their
  full width at half maximum (FWHM). Gaussian profiles appear to give the closest
  fit to the data (see Figure~\ref{fig:fwhm_fits}). We calculated all of FWHMs in
  Table~\ref{table:perfect_size_dependence} using gaussian fits.

  \textbf{IMPORTANT}: Note that the FWHM does not translate to the peak widths
  that are seen experimentally. Rather it is a measure of the decay in the
  intensity of the off center peaks. Experimentally, the center peak is the only
  peak that appears and it is broadened. If the peaks here showed up
  experimentally, they would appear as dots parallel to the $q_r$ axis, crossing
  through R-$\pi$ and in line with R-pores. There is some evidence of this
  occuring in some of the simulations (ordered parallel displaced for example).

@@

  The distance between pores does not affect the FWHM of the R-$\pi$ 'peak' in
  the $q_y$ direction.  We held the size of the unit cell constant at 42.5 x 42.5
  x 3.7 nm and varied the number of pores (and consequently, the distance between
  pores). We generated error bars for the fits based on the covariance of the
  optimized fit parameters. There is no statistical difference between the
  calculated values of each FWHM (Table~\ref{table:randomly_displaced_columns}).
  The uncertainty is lower for systems with less pores since there are more
  peaks available for curve fitting.

@@

  The real system is far from a perfect crystal. In the proceeding section, we
  explore the influence of 4 sources of disorder on the intensity of R-$\pi$:
  \begin{enumerate}
  \item Random z-displacement of columns with respect to all other columns
  \item Random rotation of layers about the z-axis
  \item Thermal noise
  \item Finite correlation between scatterers in the z-direction
  \end{enumerate}

@@

  When d = 3.7 \AA, meaning columns are completely uncorrelated, the intensity
  of R-$\pi$ is equal to the number of scatterers per column (See
  Table~\ref{table:randomly_displaced_columns}).  It is independent of the number
  of pores (and hence number of columns) in the system. The error in the
  calculated intensities are comparable to the magnitude of the intensity because
  the intensity of each configuration in the trajectory fluctuates so much.

  \begin{table}[!htb]
  \centering
  \begin{tabular}{c c c c c}
  \toprule
  $L_z$ (\AA) & Points per column & Number of Pores &  R-$\pi$ Intensity\\ 
  \midrule
  14.8        &      4            & 4               & 3.98              \\
  18.5        &      5            & 4               & 5.05              \\
  37          &      10           & 4               & 10.08             \\
  14.8        &      4            & 9               & 4.06              \\
  18.5        &      5            & 9               & 4.78              \\
  37          &      10           & 9               & 10.19             \\
  14.8        &      4            & 16              & 4.01              \\
  18.5        &      5            & 16              & 4.95              \\
  37          &      10           & 16              & 9.61              \\
  \bottomrule
  \end{tabular}
  \caption{The intensity of R-$\pi$ is equal to the number of scatters in each
	  column when columns are uncorrelated. Note that reproducing these results
	  requires a very fine histogram, and thus a much more expensive calculation. The
	  default binning scheme (100 bins in each dimension) gives slightly misleading
	  answers.
   }\label{table:randomly_displaced_columns}
  \end{table}

  \textbf{NEW} As we allow the columns to displace less (lower values of d),
  the intensity of R-$\pi$ increases (See Figure~\ref{fig:column_displacement}).
  Once there is no displacement, the intensity of R-$\pi$ matches that of a
  perfect crystal. The intensity of R-$\pi$ in the simulated system is likely
  boosted by the built-in correlation between columns.

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{column_displacement.png}
  \caption{As we increase the amount that columns are allowed to displace relative
  to each other, the intensity of R-$\pi$ decreases.}\label{fig:column_displacement}
  \end{figure}

  The $q_y$ width of R-$\pi$ is infinite when columns are randomly displaced in
  the z-direction. We attempted to measure the FWHM of the system with randomly
  displaced columns containing 4 pores and $L_z = 37$. The cross-section
  (Figure~\ref{fig:random_columns_qy}) shows non-decaying noise centered near 10,
  the same R-$\pi$ intensity measured and shown in
  Table~\ref{table:randomly_displaced_columns}. The angle averaged pattern
  (Figure~\ref{fig:random_columns_rzplot}) further illustrates the diffraction
  lines which characterize this type of system.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_columns_qy.png}
  \caption{}\label{fig:random_columns_qy}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_columns_rzplot.png}
  \caption{}\label{fig:random_columns_rzplot}
  \end{subfigure}
  \caption{When columns are uncorrelated, (a) the FWHM of the $q_y$
	  cross-section of the structure factor is infinite with a magnitude equal to the
	  number of scatterers per column. (b) The 2D structure factor angle averaged 
          about the z-axis shows diffraction lines spaced apart by 2$\pi$/d where d is the
          distance between scatterers in the z-direction.}\label{fig:random_columns_rpi_width}
  \end{figure}

@@

  \begin{table}[!htb]
  \centering
  \begin{tabular}{c c c c c c}
  \toprule
  $L_z$ (\AA) & Points per column & Number of Pores & Number of Atoms & R-$\pi$ Intensity & FWHM $\AA^{-1}$ \\
  \midrule
  14.8        &      4            & 4               & 80              &  80               & 0.37           \\
  18.5        &      5            & 4               & 100             &  100              & 0.37           \\
  37          &      10           & 4               & 200             &  200              & 0.37           \\
  14.8        &      4            & 9               & 180             &  180              & 0.37           \\
  18.5        &      5            & 9               & 225             &  225              & 0.37           \\
  37          &      10           & 9               & 450             &  450              & 0.37           \\
  14.8        &      4            & 16              & 320             &  320              & 0.37           \\
  18.5        &      5            & 16              & 400             &  400              & 0.37           \\
  37          &      10           & 16              & 800             &  800              & 0.37           \\
  \bottomrule
  \end{tabular}
  \caption{The intensity of R-$\pi$ is equal to the number of scatters in
   each column when columns are uncorrelated. Note that reproducing these results requires a very fine histogram, 
   and thus a much more expensive calculation. The default binning scheme (100 bins in each dimension) gives slightly
   misleading answers.}\label{table:randomly_rotated_layers}
  \end{table}

  In all cases, the maximum intensity of R-$\pi$ is equal to the number of
  scatterers in the system and the FWHM of the $q_y$ cross-section of the
  structure factor at R-$\pi$ is 0.37 $\AA^{-1}$
  (Figure~\ref{table:randomly_rotated_layers}), just as the perfect crystal.

  \textbf{NEW} There is no major difference in the intensity of R-$\pi$ between
  a perfect crystal and a system with randomly rotated layers. In the z
  direction, R-$\pi$ remains constant since the z components of the points are
  spaced exactly 3.7 \AA~apart. The maximum intensity of R-$\pi$ is at ($q_x,
  q_y, q_z$) = (0, 0, 1.7) so there is no contribution from the x or y
  components. Figure~\ref{fig:perfect_v_random_layers} shows a comparison of the
  cross-section of R-$\pi$ along $q_y=0$. On the surface it appears that there is
  a difference between them at high values of $q_y$. However, this is dependent
  on the initial configuration of the perfect crystal system. The system with
  randomly rotated layers will always look as it does if a sufficient number of
  configurations are included in the calculation of the structure factor. The
  perfect system is in agreement with the randomly rotated layer system at low
  values of $q_y$, corresponding to scatterers spaced far apart, however it begins
  to deviate at large $q_y$, where it describes the spatial relationship between
  scatterers in a single pore. In the perfect system, pores are randomly rotated
  with respect to each other (See Figure~\ref{fig:same_rotation}), so the spatial
  relationship changes each time a system is set up. It will not average out since
  each frame is exactly the same, but if enough pores are added, the 2 
  cross-sections will match (See Figure~\ref{fig:perfect_v_random_100pores}). 
  If we create a perfect crystal system where pores are duplicated and translated, but
  not rotated (See Figure~\ref{fig:same_rotation}), the subharmonics
  at large $q_y$ are quite pronounced (Figure~\ref{fig:perfect_crystal_same_rotation})
  due to the increase in ordering in the $q_y$ direction. The peaks are likely
  geometrically related to the spacing between points within pores, but it is 
  not important to get to the bottom of that here.

@@

  When we add z-direction gaussian noise to the lattice sites in the perfect
  crystal, the intensity of R-$\pi$ drops precipitously as noise is increased
  (Figure~\ref{fig:z_noise_perfect}).  However, the FWHM in the $q_y$ direction
  is unaffected by this noise (not pictured).

  When we add gaussian noise in the x and y directions, the intensity of
  R-$\pi$ does not change, however the FWHM sharpens with increasing noise
  (Figure~\ref{fig:xy_noise_perfect}). In other words, the intensity of
  subharmonics decrease, resulting in a smaller FWHM.

@@

  When we add noise in the x and y directions, R-$\pi$ has a finite peak width
  in its $q_y$ dimension (Figure~\ref{fig:FWHM_fit_columns}), and the intensity
  stays constant. This is different than what was previously shown
  (Figure~\ref{fig:fwhm_fits} for example). These are continuous peaks that
  represent broadening of the fundamental R-$\pi$ peak. We fit a Gaussian
  function to the the $q_y$ cross-section in order to determine its FWHM. The
  FWHM decay is inversely proportional to the amount of noise added
  (Figure~\ref{fig:FWHM_columns}).

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{random_columns_z_noise.png}
  \caption{}\label{fig:z_noise_columns}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{random_columns_gaussian.png}
  \caption{}\label{fig:FWHM_fit_columns}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{random_columns_xy_noise.png}
  \caption{}\label{fig:FWHM_columns}
  \end{subfigure}
  \caption{(a) The intensity of R-$\pi$ decays to 1 rapidly as gaussian noise is 
   added to the system. (b) When we add noise in the x and y directions, R-$\pi$
   broaden in the y-direction with a continuous intensity distribution that can be
   fit to a gaussian. (c) The FWHM decreases as the inverse of the amount of 
   noise added.}\label{fig:columns_noise}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_layers_z_noise.png}
  \caption{}\label{fig:random_layers_z_noise}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_layers_xy_noise.png}
  \caption{}\label{fig:random_layers_xy_noise}
  \end{subfigure}
  \caption{(a) As we add noise in the z-direction, the intensity of R-$\pi$ decreases
   rapidly to 1. The FWHM increases slowly and then jumps to infinity (not pictured) 
   when the intensity of R-$\pi$ becomes equal to the background intensity. However one 
   could argue there is no peak at that point. (b) When we add noise in the x and y 
   directions, the intensity of R-$\pi$ does not change, but the FWHM decays slowly.}\label{fig:layers_noise}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{covariance.png}
  \caption{An example covariance matrix used to place scatterers with a
	  correlation length. The scatterer centers are equally spaced in the
	  z-direction. Each value in the diagram represents the covariance between pairs
	  of scatterers. Diagonal entries represent covariance in position of scatterers
	  with themselves. The covariance decays exponentially as scatterers space apart
	  further.}\label{fig:covariance}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{correlation.png}
  \caption{}\label{fig:correlation_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{correlation_decay.png}
  \caption{}\label{fig:correlation_decay}
  \end{subfigure}
  \caption{(a) R-$\pi$ broadens in the $q_z$ direction when scatterers are
	  correlated. (b) The intensity of R-$\pi$ decreases as the variance in
	  scatterer position increases.}\label{fig:correlation}
  \end{figure}

@@

  \begin{table}[!htb]
  \centering
  \begin{tabular}{c c c}
  \toprule
  System                         &   $\sigma_r$ ($\AA$) &   $\sigma_z$ ($\AA$) \\
  \midrule
  Sandwiched, Ordered            &      2.30            &     1.48             \\
  Parallel Displaced, Ordered    &      2.28            &     1.45             \\
  Sandwiched, Disordered         &      2.93            &     1.58             \\
  Parallel Displaced, Disordered &      2.63            &     1.65             \\
  \bottomrule
  \end{tabular}
  \caption{Uncertainty in the deviation of monomer head groups from ideal 
          positions in each dimension for simulated LLC systems}\label{table:com_sigmas}
  \end{table}

@@

  The intensity of R-$\pi$ is strongly dependent on the initial configuration.
  Each time a model system is generated, the initial configuration is different
  than the previous model system. The thermal noise added does not compensate for
  these differences. We ran 40 different model systems with the only difference
  being the initial configuration randomization. The average R-$\pi$ intensity of
  the 40 trials was 25.7 $\pm$ 9.4. This spread has important implications for
  the reproducibility of our data since there is velocity randomization during
  the initial equilibration that will randomize the configurations which are 
  then locked in. Also, this initial configuration dependence is not
  very useful for analyzing trends.

@@

  A number of factors influence the shape and intensity of the R-$\pi$ reflection
  in our simulated systems.

  The maximum intensity of the reflection is most strongly influenced by
  disorder in the z-direction. The first source of z-directional disorder is
  caused by randomization of the initial configuration.  This configuration gets
  essentially locked into place. The second source is thermal noise during the
  simulation. The amount of thermal noise is smaller in magnitude than the
  randomization induced during early equilibration.

  The peak is broadened in the $q_y$ ($q_r$) direction when there is
  xy-direction thermal disorder in systems with randomly displaced columns. The
  peak looks most like experiment when columns are completely independent.

  The peak is broadened in the $q_z$ direction when there is a finite (non-zero)
  correlation length between scatterers.
